---
title: "Stock Price Project"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

# The idea

I want to try and practice my Machine Learning skills on financial data
To do so, I wanted to try and use a dataset of 100 variables to predict some stock prices.
I thought of trying to predict medical/Agri stocks, so I chose: 

1. TEVA     [TEVA]
2. Bayer    [BAYRY]
3. Pfizer   [PFE]
4. Protalyx [PLX]
5. Kamada   [KMDA]

Don't use because they're either private or owned by something bigger: 
Netafim, ADAMA

I thought of using these parameters: 
Dollar, Euro, Shekel prices
Major stock market indicators: NASDAQ
Specific stocks like "top-30 pharma"
Weather indicators like amount of rain in NYC (this is to see if it will be excluded)

# Notes and tips from Ran: 
* Maybe start with something less chaotic than stocks. Stocks like TEVA are affected by human elements like a CEO descision or a flop product or a scandal. 
* Try and predict oil or cotton prices. if you can do that you could be pretty rich
* Anything you try will always be difficult to predict, FYI

* I thought about doing something like extreme weather to predict oil. Let's say you have a draught and that causes oil demand to peak (for some unknown reason), you can then predict the next draught and go into oil and make a bundle in a year (or fail miserably).
* Keep in mind, good data is hard to get. stocks, currency and weather are easy to google


# Targets to predict
I want to try and predict, looking only up to Jan 2019, what will be the stock prices of the 5 companies over the course of 3 months of 2019.
So my predictions will try and project: 
closing Stock prices, per week (thursday), for 15 weeks for the following 5 companies: 

1. TEVA     [TEVA]
2. Bayer    [BAYRY]
3. Pfizer   [PFE]
4. Protalyx [PLX]
5. Kamada   [KMDA]

# Input data

For this, I want to choose 100 parameters. they may have completely differnt scales but all must change over TIME.

n  | Data    | # of parameters
---|---------|----------------
1| Historical data for all companies up to and including December 2018 | 5
2| Currency goods prices for dollars, Euro, Shekels, Yen| 3
3| Goods prices: Oil, Gold, Cotton, Corn, roses|5
4| Competitor prices for Gilead, Novartis, Monsanto, 




# Test run on loading data
## date: 20/04/2020

I collected these elements from the web: 
Index data from https://us.spindices.com/indices
Specific stock prices from Yahoo finance.

I have: 
indices:
```{r}
list.files("C:/Users/anakar/Desktop/Scratchboard/Stock prices/Input Data/Indices")
```
Stocks: 
```{r}
list.files("C:/Users/anakar/Desktop/Scratchboard/Stock prices/Input Data/competitors")
list.files("C:/Users/anakar/Desktop/Scratchboard/Stock prices/Input Data/target firms")
```

So all in all I have: 
```{r echo=FALSE}
index_num = length(list.files("C:/Users/anakar/Desktop/Scratchboard/Stock prices/Input Data/Indices"))
compet_num = length(list.files("C:/Users/anakar/Desktop/Scratchboard/Stock prices/Input Data/competitors"))
target_num = length(list.files("C:/Users/anakar/Desktop/Scratchboard/Stock prices/Input Data/target firms"))
num_of_param = index_num+compet_num+target_num
print(num_of_param)
```

### Importing the data
I'll start with the indices
Their structure is .xls files, 
where the info starts at row 8, and I want only columns A and C (date and Consumer index)

This is what I wrote today: 

The first one is only for the Dow Jones U.S. Index 
```{r}
#### Importing Xls files #######

library("readxl")
library(ggplot2)

#This imports just the first one, as a test.

dow_jones = as.data.frame(read_xls    # To import file
                          ("C:/Users/anakar/Desktop/Scratchboard/Stock prices/Input Data/Indices/DJUSI - Dow Jones U.S. Index.xls",
                            range = "A8:C5000", col_names = F))
dow_jones[,2] = NULL                        # to delete the not-needed column
colnames(dow_jones) = c("Date", "index")    # changes col names
head(dow_jones)                             # a look at the product
dim(dow_jones)

dow_jones_plot = ggplot(dow_jones,aes(x=Date,y=index)) + geom_point()

dow_jones_plot
```

And now to plot all 6 indices


```{r echo=FALSE}
#Now to get all 6 indices

index.path = "C:/Users/anakar/Desktop/Scratchboard/Stock prices/Input Data/Indices"
index.files = list.files("C:/Users/anakar/Desktop/Scratchboard/Stock prices/Input Data/Indices")

index.files
df = dow_jones
df$file = "test"

for(i in 1:length(index.files)) {
        filename = index.files[i]
        file = paste(index.path, filename, sep = "/")
        read = as.data.frame(read_xls(file, range = "A8:C5000", col_names = F))
        read[,2] = NULL
        colnames(read) = c("Date", "index")
        read$file = filename
        df = rbind(df,read)
}

#This is just a quality control
      head(df)
      dim(df)
      dim(dow_jones)

# to make the filenames into categories      
df$file = as.factor(df$file)
levels(df$file)
df$name = substr(df$file, start = 1, stop = 5)

list = df$file == "test"
### I wanted to use this to delete the test run, but I don't have time


# And now plotting
plot.indices = ggplot(df, aes(x=Date, y=index, col=name)) + geom_point()

plot.indices +theme_bw(base_size = 20) + theme(legend.position="bottom")
```


## Date: 20/04/21
starting 15:15

What I want to do: 
0. Find goods data
1. take out the "test" data in the index df
2. load the competitors data in

### Find goods data
found it at https://www.indexmundi.com/commodities/?commodity=corn&months=120
Downloaded: 
  Food:       Corn, Tea, Rice, Beef
  Industrial: Oil, Gold, Aluminum
  
  
### Taking out the "test" data in the index df

Updated R [like this](https://www.linkedin.com/pulse/3-methods-update-r-rstudio-windows-mac-woratana-ngarmtrakulchol/)

Vered woke up, and I was with her for 20 mins

```{r}
### To take out the rows which are called "test" I want to make a vector of them and then nullify in df.

test.vector = df$file == "test"    #This creates a true/false vector for the rows with "test"
summary(test.vector)               # QC: to see the number of rows to be deleted
dim(dow_jones)                     # QC: the number of rows in the original dow jones file
df.clean = df[!test.vector, ]

dim(dow_jones)+dim(df.clean) == dim(df)   #QC before gettting rid of the old rows
df = df.clean
```




### Load the competitors data in
I first will look at the data themselves.
Much nicer!
* .CSV files
* 7 columns, but I only want the date and closing, so 1 and 5
let's start: 

```{r}
#### Importing competitor files #######


#This imports just the first one, as a test.

comp.stock = read.csv("C:/Users/anakar/Desktop/Scratchboard/Stock prices/Input Data/Competitors/Galaxosmith-GLX.csv", header = T)[,c(1,5)]


head(comp.stock)                             # a look at the product
colnames(comp.stock)
dim(comp.stock)

GLX_plot = ggplot(comp.stock,aes(x=Date,y=Close)) + geom_point() + labs(title="GLX stock price")

GLX_plot
```

This doesn't look right... let me check in excel if it looks different.
Okay I checked. It's correct.

now to get them all in: 

```{r}
#Now to get all 3 competitors

comp.stock.path = "C:/Users/anakar/Desktop/Scratchboard/Stock prices/Input Data/Competitors"
comp.stock.files = list.files(comp.stock.path)

comp.stock.files
comp.stock.df = comp.stock
comp.stock.df$stock = "GSK"

head(comp.stock.df)

for(i in 1:length(comp.stock.files)) {
        filename = comp.stock.files[i]
        file = paste(comp.stock.path, filename, sep = "/")
        read = read.csv(file, header = T)[,c(1,5)]

        read$stock = filename
        comp.stock.df = rbind(comp.stock.df,read)
}

#This is just a quality control
      head(comp.stock.df)
      dim(comp.stock.df)
      dim(comp.stock)

# to make the filenames into categories      
comp.stock.df$stock = as.factor(comp.stock.df$stock)
levels(comp.stock.df$stock)
#######comp.stock.df$stock = substr(df$file, start = -5, stop = -8)


dim(comp.stock.df)
head(comp.stock.df)

class(comp.stock.df)
levels(comp.stock.df$stock)
df = comp.stock.df
df
levels(df$stock)=c("GSK","GSK2","NVS","PLX")
levels(df$stock)

# Now let's take out GSK1

takeout = df$stock == "GSK2"
#takeout

df = df[!takeout,]
summary(df$stock)
summary(df$Close[df$stock == "GSK"])


df = comp.stock.df
df = df[!takeout,]
summary(df$stock)
summary(df$Close[df$stock == "ProtalixPLX.csv"])

df$Date = as.Date(df$Date, format='%Y-%m-%d')

# Make shorter names
df$filename = df$stock
levels(df$stock) = c("GLS","test", "NVS", "PLX")

# And now plotting
plot.comp.stock = ggplot(df, aes(x=Date, y=Close, col=stock)) + geom_point()

plot.comp.stock.formatted = plot.comp.stock +theme_gray(base_size = 20) + theme(legend.position="right", axis.text.x = element_text(angle = 90)) + scale_x_date(date_labels = "%Y")
comp.stock.df = df

```


So, I'm stopping now. This is not clean but getting there...
Updating R screwed up the ggplot somehow...
knit and out
16:40

## New day
What do I want to do today?
1. Fix the scale for the last figure - done and put into the old code

    Alright, I fixed a stupid bug. In the line to read the new files I had a specific file loaded up each time... nevermind, moving forward. Here's the graph: 

```{r}
plot.comp.stock.formatted
```



2. make a correlation map so that I can see correlations between different data

Let's start with the weird formatting and scale from last time
```{r}
sum.GLS = summary(df$Close[df$stock == "GLS"])
sum.NVS = summary(df$Close[df$stock == "NVS"])
sum.PLX = summary(df$Close[df$stock == "PLX"])

stock.GLS = df$Close[df$stock == "GLS"]
stock.NVS = df$Close[df$stock == "NVS"]
stock.PLX = df$Close[df$stock == "PLX"]
print(sum.GLS)
print(sum.NVS)
print(sum.PLX)

class(df$Close[df$stock == "GLS"])

cor(stock.GLS,stock.NVS)

closing = data.frame(cbind(stock.GLS, stock.NVS,stock.PLX))

dim(closing)
colnames(closing)
cor.matrix = cor(closing)
```
Now to make it into a heatmap: 
```{r}
	if (!requireNamespace("BiocManager", quietly = TRUE))
	        install.packages("BiocManager")
	BiocManager::install()
	
	BiocManager::install(c("ComplexHeatmap", "AnnotationDbi"))
	
	
	
	library(ComplexHeatmap)





Heatmap(cor.matrix, 
        cluster_columns=FALSE,
        cluster_rows=FALSE
)


```


So - I finished what I wanted.
This took ~1.5 hours but looks nice, no?
Knit.






# New day!
What do I want to do today?
Finish loading up different data: 
- goods data
- 5 more stock data
- target stock data

let's start by loading in 5 more stock data for these companies: 
1. Gilead [GILD]
2. CARL ZEISS MEDITEC
3. Syngenta AG - PRIVATE, no prices
3. Coca Cola [KO]
4. Merck
5. Compugen

I need to first download their prices - Done, from www.finance.yahoo.com

Now let's load it in
```{r}

```